Suitability of Graph Neural Network for Shape Memory Alloys

### 2024-04-08 src/tex/ms.tex
Fix name of figure again arrgggit add src/tex/ms.tex
Fix name again :(.
Update plotting. Some new text.

\title{Qualitative Assessesment of Graph Neural Network Potentials for
	Phonon Properties of Shape Memory Alloys using Graph Neural Network
	Potentials}

@@

\begin{figure}[ht!]
	\label{fig:opt_density}
	\centering
	\includegraphics[options]{figures/NiTi_Equilibrium_Density.png}
	\caption{Equilibrium Density for \ce{NiTi} structures with different
		models.}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B2_ModelsPhononBandstructure.png}
		\caption{ Ground-state, no isotropic strain, Phonon bandstructure
			of B2 phase for all models. The Mutter and Zhong EAM potentials
			differ in that Mutter predicts no dynamic instability of the B2
			phase at 0K.  }
		\label{fig:allmodels_b2}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of B19 phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19P_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of
			\textit{B19}$^\prime$ phase for all models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_BCO_ModelsPhononBandstructure.png}
		\caption{ Ground-state phonon bandstructure of BCO phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

>>>>

\title{Suitability of Graph Neural Network for Shape Memory Alloys}

@@

\begin{figure}[ht!]
	\label{fig:opt_density}
	\centering
	\includegraphics[width=\linewidth]{figures/NiTi_Equilibrium_Density.png}
	\caption{Equilibrium Density for \ce{NiTi} structures with different
		models.}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B2_ModelsPhononBandstructures.png}
		\caption{ Ground-state, no isotropic strain, Phonon bandstructure
			of B2 phase for all models. The Mutter and Zhong EAM potentials
			differ in that Mutter predicts no dynamic instability of the B2
			phase at 0K.  }
		\label{fig:allmodels_b2}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19_ModelsPhononBandstructures.png}
		\caption{ Ground-state phonon bandstructure of B19 phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_B19P_ModelsPhononBandstructures.png}
		\caption{ Ground-state phonon bandstructure of
			\textit{B19}$^\prime$ phase for all models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=\linewidth]{figures/NiTi_BCO_ModelsPhononBandstructures.png}
		\caption{ Ground-state phonon bandstructure of BCO phase for all
			models.  }
		\label{fig:allmodels_B19P}
	\end{centering}
\end{figure}
